Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
more

\begin{table*}[t]
\center
\footnotesize
% \setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Summary of Micro-benchmarks}.
    The micro-benchmarks are small pipelines (\ie ones developed on-the-fly) drawn from various sources and applied to large datasets.
  }
}
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} llllll}
\toprule
  Script                 ~&~ Structure                    & Input (MB)& Time (Seq)    & Script Size (LoC)             & Highlights                                        \\
\midrule
% https://github.com/andromeda/sdsh/blob/master/scripts/grep.sh
  \tti{grep}         ~&~$3\times$\tsta                & 1000      &  78m 36.77s   &   30\qquad 134\qquad  1304    & complex NFA regex                                 \\
% https://github.com/andromeda/sdsh/blob/master/scripts/minimal5.sh
  \tti{sort}         ~&~~$\tsta, \tpur$               & 10000     &  23m 19.85s   &   33\qquad 129\qquad  1209    & \tti{sort}ing                                     \\
% https://github.com/andromeda/sdsh/blob/master/scripts/topn.sh
  \tti{wf}               ~&~~$3\times\tsta, 3\times\tpur$ & 1000      &   2m 11.18s   &   53\qquad 181\qquad  1621    & double \tti{sort}, \tti{uniq} reduction           \\
% https://github.com/andromeda/sdsh/blob/master/scripts/topn.sh
  \tti{top-n}            ~&~~$2\times\tsta, 4\times\tpur$ & 1000      &   6m 53.55s   &   53\qquad 181\qquad  1621    & double \tti{sort}, \tti{uniq} reduction           \\
% https://github.com/andromeda/sdsh/blob/master/scripts/ngrams.sh
  \tr{\tti{bi-gram}          ~&~~$2\times\tsta, 4\times\tpur$ & \todo{X}  &               &   X \qquad  X \qquad          & stream shifting and merging                       \\}
% https://github.com/andromeda/sdsh/blob/master/scripts/spell.sh
  \tti{spell}            ~&~~$4\times\tsta, 3\times\tpur$ & 1000      &   8m 13.42s   &  37 \qquad 257\qquad  2417    & comparisons (\tti{comm})                          \\
% https://github.com/andromeda/sdsh/blob/master/scripts/diff.sh
  \tr{\tti{diff}             ~&~~$4\times\tsta, 3\times\tpur$ & \todo{X}  &               &   X \qquad  X \qquad          & shuffling and non-distributable \tti{diff}ing     \\}
  \tti{shortest-scripts} ~&~~$5\times\tsta, 2\times\tpur$ & 8.6       &   2m 50.03s   &  61 \qquad 253\qquad  2413    & \todo{x}                          \\
\bottomrule
\end{tabular*}
\label{tab:eval}
\end{table*}

@@

The complex macro-benchmark (\S\ref{macro1}) is designed to handle realistic workloads by today's standards.
It is about an order of magnitude larger than the micro-benchmarks, but this perceived lack of complexity is deceiving:
  as shown below, if written in conventional languages, this pipeline would correspond to a program on the order of hundreds of lines of code.

@@

In terms of benchmarks, \ttt{grep} is a short script centered around an expensive \sta command.
% a DFA-based regular expression matching phase;
  while \ttt{grep} defaults to a Thompson NFA, this particular expression makes use of DFA-based backtracking patterns resulting in high runtime overhead.
The \ttt{sort} pipeline is equally short, but its central operation is a command in \pur.
The next two benchmarks, \ttt{wf} and \ttt{top-n}, are based on McIlroy's now classic word-counting program~\cite{bentley1986literate};
  they use sorting, rather than tabulation, to identify high-frequency terms in a corpus.
\tr{The \ttt{bi-gram} pipeline calculates n-grams of base two;
  it makes clever use of \ttt{tail} to shift a stream by one word and \ttt{paste} to fuse (zip) two streams together.}
The next pipeline is based on the original \ttt{spell} program developed by Johnson~\cite{bentley1985spelling}---another \unix classic:
  after some preprocessing, it makes clever use of \ttt{comm} to report words not in the dictionary.

>>>>

\begin{table*}[t]
\center
\footnotesize
% \setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Summary of Micro-benchmarks}.
    The micro-benchmarks are small pipelines (\ie ones developed on-the-fly) drawn from various sources and applied to large datasets.
  }
}
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} llllll}
\toprule
  Script                 ~&~ Structure                    & Input (MB)& Time (Seq)    & Script Size (LoC)             & Highlights                                        \\
\midrule
% https://github.com/andromeda/sdsh/blob/master/scripts/grep.sh
  \tti{grep}         ~&~$3\times$\tsta                & 1000      &  78m 36.77s   &   30\qquad 134\qquad  1304    & complex NFA regex                                 \\
% https://github.com/andromeda/sdsh/blob/master/scripts/minimal5.sh
  \tti{sort}         ~&~~$\tsta, \tpur$               & 10000     &  23m 19.85s   &   33\qquad 129\qquad  1209    & \tti{sort}ing                                     \\
% https://github.com/andromeda/sdsh/blob/master/scripts/topn.sh
  \tti{wf}               ~&~~$3\times\tsta, 3\times\tpur$ & 1000      &   2m 11.18s   &   53\qquad 181\qquad  1621    & double \tti{sort}, \tti{uniq} reduction           \\
% https://github.com/andromeda/sdsh/blob/master/scripts/topn.sh
  \tti{top-n}            ~&~~$2\times\tsta, 4\times\tpur$ & 1000      &   6m 53.55s   &   53\qquad 181\qquad  1621    & double \tti{sort}, \tti{uniq} reduction           \\
% https://github.com/andromeda/sdsh/blob/master/scripts/ngrams.sh
  \tr{\tti{bi-gram}          ~&~~$2\times\tsta, 4\times\tpur$ & \todo{X}  &               &   X \qquad  X \qquad          & stream shifting and merging                       \\}
% https://github.com/andromeda/sdsh/blob/master/scripts/spell.sh
  \tti{spell}            ~&~~$4\times\tsta, 3\times\tpur$ & 1000      &   8m 13.42s   &  37 \qquad 257\qquad  2417    & comparisons (\tti{comm})                          \\
% https://github.com/andromeda/sdsh/blob/master/scripts/diff.sh
  \tr{\tti{diff}             ~&~~$4\times\tsta, 3\times\tpur$ & \todo{X}  &               &   X \qquad  X \qquad          & shuffling and non-distributable \tti{diff}ing     \\}
  \tti{shortest-scripts} ~&~~$5\times\tsta, 2\times\tpur$ & 8.6       &   2m 50.03s   &  61 \qquad 253\qquad  2413    & extensive file-system operation   \\
\bottomrule
\end{tabular*}
\label{tab:eval}
\end{table*}

@@

The complex macro-benchmark (\S\ref{macro1}) is designed to handle realistic workloads by today's standards.
It is about an order of magnitude larger than the micro-benchmarks, but its perceived lack of complexity is deceiving:
  as shown if written in a conventional language, it correspond to a program on the order of hundreds of lines of code.

@@

In terms of benchmarks, \ttt{grep} is a short script centered around an expensive \sta command;
% a DFA-based regular expression matching phase;
  while \ttt{grep} defaults to a Thompson NFA, this particular expression makes use of DFA-based backtracking patterns resulting in high runtime overhead.
The \ttt{sort} pipeline is equally short, but its central operation is a command in \pur.
The next two benchmarks, \ttt{wf} and \ttt{top-n}, are based on McIlroy's now classic word-counting program~\cite{bentley1986literate};
  they use sorting, rather than tabulation, to identify high-frequency terms in a corpus.
% \tr{The \ttt{bi-gram} pipeline calculates n-grams of base two;
%   it makes clever use of \ttt{tail} to shift a stream by one word and \ttt{paste} to fuse (zip) two streams together.}
The next pipeline is based on the original \ttt{spell} program developed by Johnson~\cite{bentley1985spelling}---another \unix classic:
  after some preprocessing, it makes clever use of \ttt{comm} to report words not in the dictionary.
Finally, \ttt{shortest-scripts} is a pipeline~\cite[pg. 7]{taylor2004wicked}that identifies the 15 shortest shell scripts in the user's \ttt{PATH};
   interestingly, it uses \ttt{file} utility and a higher-order \ttt{wc}.
